---
title: "Making a website on GitHub"
author: "Erik Schoen"
date: "10/17/2018"
output: 
  html_document:
    toc: yes
    toc_float: yes
    number_sections: yes
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# A simple data analysis using salmon escapement data

##Load packages
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(readr)
library(leaflet)
library(DT)
```

##Read in data
Next, read in some escapement data: [Alaska Department of Fish and Game. 2017. Daily salmon escapement counts from the OceanAK database, Alaska, 1921-2017. Knowledge Network for Biocomplexity. doi:10.5063/F1TX3CKH.](https://knb.ecoinformatics.org/knb/d1/mn/v2/object/urn%3Auuid%3Af119a05b-bbe7-4aea-93c6-85434dcb1c5e)

```{r read in data}
esc <- read_csv("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/urn%3Auuid%3Af119a05b-bbe7-4aea-93c6-85434dcb1c5e")
head(esc)
```

Calculate annual median escapement by species
```{r}
esc_annual <- esc %>%
  separate(sampleDate, into = c("Year", "Month", "Day"), sep = "-") %>%
  group_by(Species, Year) %>%
  summarize(AnnualCount = sum(DailyCount))
head(esc_annual)

esc_annual_medians <- esc_annual %>%
  group_by(Species) %>%
  summarize(MedianEsc = median(AnnualCount))
datatable(esc_annual_medians)
```

Make a bar plot
```{r}
esc_median_barplot <- ggplot(data = esc_annual_medians, aes(x = Species, 
                                                            y = MedianEsc)) +
  geom_bar(stat = "identity") +
  coord_flip()
esc_median_barplot
```


# Map the bad boy using `leaflet`

## Clean the data
Remove columns we don't need and keep only one row for each location.

```{r clean the location data}
locations <- esc %>%
  select(Location, SASAP.Region, Latitude, Longitude) %>%
  distinct() %>%
  # remove locations without lat/lons
  drop_na()
```

## Make the map
```{r}
leaflet(locations) %>%
  addTiles() %>%
  # Need to add ~ (tildes) in front of the arguments for some unknown reason!
  addMarkers(lat = ~Latitude, lng = ~Longitude, popup = ~Location)
```

